### 2021-04-15 papers/SYRCoSE/overview.tex
overview: minor

@@

Finally, we use yet another feature of \mathcomp --- 
\emph{packed classes}~\cite{Garillot-al:ICTPHOL2009}, 
in order to encode the algebraic hierarchy
of various classes of event structures.

>>>>

In fact, binary relations are omnipresent in our formalization.
In order to further automate the reasoning about them, 
we have chosen to use the \relationalgebra%
\footnote{\url{https://github.com/damien-pous/relation-algebra}}~%
\cite{Pous-ITP2013} package 
which provides a number of tactics to solve goals using
decision procedures for the theory of lattices  
and \emph{Kleene Algebras with Tests}~\cite{Kozen:TOPLAS:1997}.

@@

To facilitate computable semantics, we define a subclass of
finitely supported event structures as a finite sequence of events
combined with finitely supported function which enhance events with 
additional information, such as their labels, causality predecessors, \etc 
Encoding finitely supported functions is not a trivial endeavor in
a proof assistant and for this task we use the \finmap~%
\footnote{\url{https://github.com/math-comp/finmap}}
library which is an extension of \mathcomp~providing finite sets and
finite maps on types with a choice opeartor (rather than on finite types).

Finally, to encode the algebraic hierarchy of various classes of event structures
we use yet another feature of \mathcomp~--- 
\emph{packed classes}~\cite{Garillot-al:ICTPHOL2009},
which is a design pattern providing multiple inheritance,
maximal sharing of notations and theories,
and automated structure inference. % and it also deals with performance issues.

% TODO
% The relation-algebra package and lattice theory
% well-foundedness and transitive closure for boolean relations
% identType and how to fight quadratic time complexity
